Approximation as Differentiation

### 2025-07-08 main/approx-as-tangents.tex
Improve some citations.

\emph{Stability} is a property that can be required of monotone functions that was invented by \citet{berry79} in an attempt to capture sequentiality. This was not successful (see the $\mathrm{gustave}$ function in \exref{parallel-or}), but we will see now how it is closely related to problem of computing forward and backwards maps of approximations needed in \GPS. A textbook description of stable functions in the context of domain theory is given by \citet{amadio-curien} (Chapter 12). We start with a property that is weaker than stability, but is easier to motivate in connection with derivatives of smooth functions.

@@

  Relatedly, \citet{edalat-heckmann98} proposed a Scott domain of
  formal balls on a metric space, where again the maximal elements are
  the points of the original space. More generally,
  \citet{continuous-lattice-book} (Section V-6) describe \emph{domain
    environments}, which are domains whose maximal elements are
  exactly the points of a topological space. We are not aware of any
  work linking domain environments in general to stable functions. It
  would be interesting to see whether the situation for intervals,
  where approximations must be relative to a nominated point, repeats
  in general when considering conditionally multiplicative functions.
\end{example}

>>>>

\emph{Stability} is a property that can be required of monotone functions that was invented by \citet{berry79} in an attempt to capture sequentiality. This was not successful (see the $\mathrm{gustave}$ function in \exref{parallel-or}), but we will see now how it is closely related to problem of computing forward and backwards maps of approximations needed in \GPS. A textbook description of stable functions in the context of domain theory is given by \citet[Chapter 12]{amadio-curien}. We start with a property that is weaker than stability, but is easier to motivate in connection with derivatives of smooth functions.

@@

  Relatedly, \citet{edalat-heckmann98} proposed a Scott domain of
  formal balls on a metric space, where again the maximal elements are
  the points of the original space. More generally,
  \citet[Section V-6]{continuous-lattice-book} describe \emph{domain
    environments}, which are domains whose maximal elements are
  exactly the points of a topological space. We are not aware of any
  work linking domain environments in general to stable functions. It
  would be interesting to see whether the situation for intervals,
  where approximations must be relative to a nominated point, repeats
  in general when considering conditionally multiplicative functions.
\end{example}
